---
title: "esm206-lab7-cje-MLR"
author: "Chance English"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)


library(tidyverse)
library(here)
library(palmerpenguins)
library(ggplot2)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```



### Intro to GGally : ggpairs() function to create a pairs plot

```{r}

ggpairs(penguins)





```


```{r}
 
penguins %>% 
  select(species, bill_length_mm: body_mass_g) %>% 
  ggpairs(aes(color = species))


penguins %>% ggplot(aes (x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth( method = "lm")


# Simpsons Paradox; relationship reverses if we don't account for some variable (in this case not including species as a vairbale results in a negative relationshop between bill depth and body mass)

```


## Multiple Linear Regression - penguins

Use MLR to try to understand the relaitonshio between multiple predictor variables and a single continuous outcome variable (body mass)

```{r}

penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)


plot(penguin_lm)

penguin_lm

```


How would you interpret this coefficient for flipper_length_mm?

We would expect, on average, a 51.54 g increase in penguin body mass for each 1mm increase in flipper length, if evertything else is held constant 


### Use summary() function to get more information on the model

```{r}

summary(penguin_lm)


```

A non-significant coefficient does not mean that you should drop that value from the model


#### Use the 'broom' functions tidy and glance 

Use broom::tidy to get the coefficient summary in a data frame
Use broom:glance to get the model summary ina  data frame 



```{r}

penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy




```

For each mm increase in bill depth length, on average555 there is a `r round(penguin_lm_tidy$estimate[3], 1)` g increase in penguin body mass. 




## Try another model

We've thought alot of about it... the 3 best variables to include in the model are 

- flipper length
- species
- sex 

Task: create a MLR regression model using those 3 predictor variables 



```{r}

penguins_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguins_lm_2

summary(penguins_lm_2)

penguins_lm_2_tidy <- tidy(penguins_lm_2)
penguins_lm_2_tidy
```


bodymass = 365.82 + 20.02*flipperlenghth - 87.63*chinstrap + 836.26*gentoo + 530.38*male 

Interpreting coefficients with a reference level 

If everything else is the same then on average we expect a gento penguin to weigh 836.26 g more than an adelie 
Chinstrap penguins we expect to be 87.63 g less than an adelie 

Predict the mass of a penguin that has a flipper length of 180 mm that is a chinstrap penguin that is female you would plug in a 1 or 0 to evaluate the model 

Estimate body mass of an male adelie penguin with flippers thate were 200 mm long 

Body Mass = `r mass = 365.82 + 20.02 * 200 + 0*-87.63 + 0*836.26 + 530.38 ` = 4900.2 g


Need to look at the residuals to evaluate the model
  - normal
  -homoscadasticity 

```{r}
augment(penguins_lm_2)

# Compare real data to fitted model

```

```{r}

plot(penguins_lm_2)


```

- QQ Plot: residuals are normally distributed (plot 2)
- Plot 1 & 3; vertical distribution of values (residuals) are constistently spread across the model
- Shows any points pulling a disproportional amount of weight 
- Conceptual Understanding and expertise that allow me to responsible determine that penguin species, sex and flipper length are reasonable predictor variabless



## Make output tables 

Using Model Summary
```{r}
 
modelsummary(penguins_lm_2)


```





Using Stargazer 

```{r, results="asis"}

stargazer(penguins_lm_2, type = "html")

# Need to include asis in the set up as knit will try to render an html but its already an html

```

